### 2018-04-04 ms/ms_probaweb.tex
typos on the ms

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{color,lineno,setspace,multirow}
\usepackage{graphicx}
\usepackage[top=2.4cm,left=2.4cm,top=2.4cm,bottom=2.4cm,includefoot]{geometry}
\usepackage{natbib}
\usepackage{caption}
\usepackage{pdflscape}
\usepackage{hyperref}

@@

Biogeography has traditionally focused on the spatial distribution and
abundance of species. Both are driven by the way species interact with one
another, but also by the way these interactions vary across time and space.
Here, we call for an integrated approach, adopting the view that community
structure is best represented as a network of ecological interactions, and
show how it translates to biogeography questions. We propose that the
ecological niche should encompass the effect of the environment
on species distribution (the Grinnellian dimension of the niche) and on the
ecological interactions among them (the Eltonian dimension). Starting from
this concept, we develop a quantitative theory to explain turnover of
interactions in space and time -- \emph{i.e.} a novel approach to interaction
distribution modelling. We apply this framework to host–parasite interactions
across Europe and find that two aspects of the environment (temperature and
precipitation) exert a strong imprint on species co-occurrence, but not on
species interactions. Even where species co-occur, interaction proves to be
stochastic rather than deterministic, adding to variation in realized network
structure. We also find that a large majority of host-parasite pairs are never
found together, thus precluding any inferences regarding their probability to
interact. This first attempt to explain variation of network structure at
large spatial scales opens new perspectives at the interface of species
distribution modelling and community ecology.

@@

Community ecology is \textit{the study of the interactions that determine the
distribution and abundance of organisms} \citep{Krebs2001}. Despite a general
consensus on this definition \citep{Scheiner2007a}, research on variation in
community structure (beta-diversity) has mostly focused on the spatial and
temporal turnover of species composition \citep{Anderson2011}. Such research
usually neglects variation in the way species interact with each other,
despite accumulating empirical evidence that this is a major source of
diversity \citep{Poisot2015a}. Given this omission, it is perhaps not
surprising that biogeographers are still struggling to establish whether
interactions actually impact the distribution of species at large spatial
scales \citep{Kissling2012}. An interaction is conceived as the direct effect
of the action of one species on the demography on another species; whether it
scales up and impact the (co-)distribution of species remains matter of debate
at the moment \citep{Wisz2012, GonzalezSalazar2013, Cazelles2016b,
Harris2016, Godsoe2017}. Treating interactions as fixed events nonetheless
neglects a large part of the complexity of empirical communities, and will
most likely deliver underwhelming results \citep{Poisot2015c}. Recent attempts
at accounting for interactions in species distribution models
\citep{Pollock2014, Pelissier2013, Ovaskainen2017} have brought some
methodological advances, but are not sufficient for two reasons. First, these
techniques are still based on a `species-based' approach to communities, where
interactions are merely treated as fixed covariates affecting distribution.
Second, they failed to provide a conceptual step forward, both in their
treatment of interactions and in the quality of the predictions they make.

Network approaches offer a convenient representation of communities because
they simultaneously account for species composition and their interactions.
Species are represented as nodes, so that networks already encompass all the
information used by current approaches of species distribution modelling; in
addition, interactions are represented by links, so that networks provide
additional information on community structure. To date, studies of network
diversity have mostly been concerned with the distribution of interactions
within locations, and less so with variation among locations \citep{Dunne2006,
Bascompte2007, Ings2009, Kefi2012}. There is, however, ample evidence that
interaction networks vary in space and, time \citep{Laliberte2010, Poisot2012,
Schleuning2012, Albouy2014, Poisot2016, Trojelsgaard2015}, even though there
is no common framework with which to generalize these results. Metacommunity
theory provides explanations for variation in the distribution of the nodes
\citep{Gravel2011c, Pillai2011,Cazelles2015}, but there is no such explanation
to the variation of node and link occurrences. Consequently, we need theory to
formalize these observations, as it is the only way towards fulfilling the
goal of community ecology: providing cogent predictions about, and
understanding of, the structure of ecological communities.

Given the historically different approaches to modelling the distributions of
species vs. interactions, there is need to bring the two together. Here, we
offer an integrated approach to do so, adopting the view that community
structure is best represented as a network of ecological interactions. Based
on this idea, we propose a description of the ecological niche that
integrates the effect of the environment on species distribution and on the
ecological interactions among them. Building on this concept, we develop a
quantitative theory to explain turnover of interactions in space and time. We
first present the concept and then formalize it mathematically, using a
probabilistic model to represent the sampling of the regional pool of
interactions. At the level of species pairs, the statistical approach could be
conceived as an interaction distribution model. At the community level, the
approach provides a likelihood-based method to compare different hypotheses of
network turnover. As an illustrative example, we apply this novel framework to
a large data set on host–parasite interactions across Europe and find that two
aspects of the environment (temperature and precipitation) exert a strong
imprint on species co-occurrence, but not on species interactions. The network
structure changes systematically across the latitudinal gradient, with a peak
of connectance at intermediate latitudes.

@@

The problem of community assembly is often formulated as \textit{how are
species sampled from a regional pool to constitute a local community
\citep{Gotzenberger2012}?} This question could be rewritten to address the
problem of network assembly, as \textit{how do samples from a regional pool of
interactions constitute a local interaction network?} An illustration of this
problem for a food web is provided in Fig. 1. The regional pool of
interactions, the \emph{metaweb}, represents potential interactions among all
species that could be found in a given area. In this particular case, there
are 275 nodes, and 1173 links among the plants (52 nodes), herbivores (96
nodes), and parasitoids (127 nodes) from Northern Europe. An instance of a
local community is also illustrated, with 45 nodes and 93 interactions. Only
55.0\% of all potential interactions (plant-herbivore or herbivore parasitoid
combinations) are realized in this local network, revealing the stochastic
nature of ecological interactions. Our objective here is to provide theory to
explain the sampling of the regional pool of interactions, along with a
quantitative method to predict it. The problem could be formalized
sequentially by understanding first why only a fraction of the species co-
occur locally and second why these species do or do not interact.

There are multiple causes of spatial turnover of species co-occurrence. The
first and most-studied driver is the effect of variation in the abiotic
environment on species performance. Combined with specific responses in
demography, it generates variation among sites by selecting the locally
fittest species \citep{Leibold2004a}. Stochasticity plays an additional role,
either because colonization and extinction events \citep{Hanski1999} are
inherently unpredictable or because strong non-linear feedbacks in community
dynamics generate alternative transients and equilibria \citep{Chase2007,
Vellend2014}. Interaction themselves may impact co-distribution, as
hypothesized long ago by Diamond \citet{Diamond1975}. Analyses of community
turnover are usually performed with data represented in a table with rows
corresponding to sites (or measurements) and columns to species. Metrics of
beta diversity quantify the variance of this community data
\citep{Legendre2005}. Traditional approaches rely on measures of dissimilarity
among communities, such as the Jaccard or Bray–Curtis indices. More recent
approaches decompose total variation of the community data into species and
site contributions to beta diversity \citep{Legendre2013}, and further
partition it into dissimilarity due to changes in species richness and
dissimilarity due to actual species turnover \citep{Baselga2010}. T Even
though all of these methods compare whole lists of species among sites or
measurements, they remain fundamentally "species-based", since they report
variation within columns. None of them explicitly considers variation of
associations (i.e., of pairs or higher-order motifs – \citealt{Stouffer2007}).
The only exceptions are the Joint Species Distribution Models
\citep{Warton2015, Ovaskainen2017}, which further account for the covariance
among species after representing their response to the environment.

Similarly, we are now getting a better understanding of interaction turnover. As
mentioned above, in the network approach to community structure, species and
interactions are represented by nodes and links, respectively. Associations
can also be represented by matrices in which entries represent the occurrence
or intensity of interactions among species (rows and columns). Network
complexity is then computed as the number of interactions (in the case of
binary networks) or interaction diversity (in the case of quantitative
networks, \citealt{Bersier2002}). Variability in community structure
consequently arises from the turnover of species composition, along with
turnover of interactions among pairs of species. The occurrence and intensity
of interactions could vary because of the environment, species abundance, and
higher-order ecological interactions \citep{Poisot2015a}. Variation in community
composition can be independent of variation of ecological
interactions, suggesting that species and interaction distribution may well
respond to different drivers \citep{Poisot2012}.

The "niche" is by far the dominant concept invoked to explain species
distributions and community assembly, from the local to the global scale.
Following \citealt{Hutchinson1957}, the niche is viewed as the set of
environmental conditions allowing a population to establish and persist (see
also \citealt{Holt2009a}). In other words, the niche is the location in that
multidimensional space that allow a species to have a positive growth rate
when rare \citep{Godsoe2017}.  Community turnover arises as a result of
successive replacement of species along an environmental gradient, in
agreement with the Gleasonian view of communities \citep{Gleason1926}. The
concept is straightforward to put into practice with species distribution
models, as it maps naturally on available distributional and environmental
data. Consequently, a vast array of statistical tools have been developed to
implement it (e.g. BIOMOD \citealt{Thuiller2003}, MaxEnt
\citealt{Phillips2006}). It is however much harder to account for ecological
interactions within this approach \citep{Peterson2011}. As such, these
interactions are often viewed as externalities constraining or expanding the
range of environmental conditions required for a species to maintain a viable
population \citep{Pulliam2000, Soberon2007}.

@@

Despite several attempts to update the concept of the ecological niche,
ecologists have not moved far beyond the "n-dimensional hypervolume" defined
by Hutchinson. Despite its intuitive interpretation and easy translation into
species distribution models \citep{Boulangeat2012, Blonder2014}, the concept
has been frequently criticized \citep{Hardin1960, Peters1991, Silvertown2004},
and several attempts have been made to expand and improve it
\citep{Pulliam2000, Chase2003, Soberon2007, Holt2009a, McInerny2012b}.

@@

These perspectives are rather orthogonal to each other, and this has resulted
in considerable confusion in the literature \citep{McInerny2012a}.
\citealt{Chase2003} attempted to reconcile with the following definition:
\emph{"[The niche is] the joint description of the environmental conditions that
allow a species to satisfy its minimum requirements so that the birth rate of
a local population is equal to or greater than its death rate along with the
set of per capita effects of that species on these environmental conditions"}.
Their representation merges zero-net-growth isoclines delimiting the
Grinnellian niche ("when does the population persists?") with impact vectors
delimiting the Eltonian niche ("what is the per-capita impact?"). While this
representation has been very influential in local-scale community ecology (the
resource-ratio theory of coexistence, \citealt{Tilman1982}), it remains
impractical at larger spatial scales because of the difficulties in measuring
it. The absence of any mathematical representation of the niche that can be
easily fit to ecological data may explain why biogeographers are still
struggling to develop species distribution models that also consider
ecological interactions. Thus, a more integrative description of the niche
will be key to understand spatial and temporal turnover in community
structure.

We propose to integrate the two perspectives of the niche using a visual
representation of both components (Fig. 2). The underlying rationale is that,
in addition to the environmental constraints on demographic performance (Fig.2
top panel), any organism requires resources to meet its metabolic demands and
to sustain reproduction (Fig. 2 nodes in network of bottom panel). Abiotic
environmental axes are any non-consumable factors affecting the demographic
performance of an organism. Alternatively, the resource axes are traits of the
resources that allow interactions with the consumers. By definition of what an
interaction is, these axes also influence the growth rate. The niche can
therefore be viewed as the set of abiotic environmental conditions (the
Grinnellian component) along with the set of traits (the Eltonian component)
that allow a population to establish and to grow at a location. This visual
representation make operational the theoretical interpretation of the niche
and species ranges by Godsoe et al. \citealt{Godsoe2017}. Accordingly, each
species can be characterized by an optimal position along both the
environmental (x-axis) and the trait (y-axis) plane. The integrated niche is
then the hypervolume where interactions can occur and where a population has a
positive growth rate.

@@

The first term on the right-hand side of the equation is the probability
of observing the two species co-occurring at location $y$. It corresponds
to the Grinnellian dimension of the niche. The second term represents the
probability that an interaction occurs between species $i$ and $j$, given that
they are co-occurring. This predicate can be refined using information on
trait distribution and trait matching rules (\citep{Bartomeus2016}).
Above, we referred to this entity as the "metaweb" and it corresponds to
the Eltonian dimension of the niche. Below, we will see how this formalism
can be directly fit to empirical data. But before turning to an application,
we will discuss the interpretation of different variants of these two terms.

@@

There are several variants to the co-occurrence probability, representing
different hypotheses concerning spatial variation in network structure (see
the explicit formulations in Table 1). The simplest model relates the
probability of co-occurrence directly to the environment,
$P(X_{iy},X_{jy}|E_y)$. In this situation, there are no underlying assumptions
about the ecological processes responsible for co-occurrence. It could arise
because interactions constrain distribution, where in such case the co-
occurrence would be conditional on $L$, or, alternatively, because of
environmental requirements shared between $i$ and $j$ \citep{Pollock2014,
Cazelles2016}. In the former case, species are not independent of each other
and the conditional occurrence must be accounted for explicitly,
$P(X_{iy},X_{jy} |E_y)=P(X_{iy}|E_y,X_{jy})P(X_{jy}|E_y)$. In the latter case,
species are independent, and only the marginal occurrence must be accounted
for, $P( X_{ijy}|E_y)=P(X_{iy} |E_y)P(X_{jy} |E_y)$.

The co-occurrence probability itself could depend on ecological interactions. 
This should be viewed as the realized component of the niche (i.e. the
distribution when accounting for species interactions). Direct pairwise
interactions such as competition, facilitation, and predation have long been
studied for their impact on co-distribution (e.g. \citealt{Diamond1975,
Connor1979, Gotelli2000}). Second- and higher-order interactions (e.g. trophic
cascades) could also affect co-occurrence \citep{Harris2017,
Staniczenko2017}. Co-occurrence of multiple species embedded in ecological
networks is a topic of its own, however, and is influenced by both network
topology and species richness \citep{Cazelles2016}. Not only direct
interactions influence co-occurrence, but indirect interactions do as well
(e.g. plant species sharing an herbivore, or herbivores sharing parasitoids,
could repel each other in space \citealt{Holt1993}). The impact of direct
interactions and first-order indirect interactions on co-occurrence tends to
vanish with increasing species richness in the community \citep{Cazelles2016}.
Further, co-occurrence is also influenced by the covariance of interacting
species to an environmental gradient \citep{Cazelles2015}.

@@

Second, ecological interactions could also vary with the environment, so that
$P(L_{ijy}|E_y)$. Although it is rare to see a conditional representation of
pairwise ecological interactions, experimental studies have frequently
revealed interactions to be sensitive to the environment. For instance,
\citep{Mckinnon2010} showed that predation risks of shorebirds vary at the
continental scale, decreasing from the south to the north. It is also common
to see increasing top-down control with temperature (e.g. \citealt{Shurin2012,
Gray2016}). Effects of the environment on interactions \citep{Gibert2014} also
propagate up the community and influence network structure
\citep{Tylianakis2007, Woodward2010, Petchey2010a}.

@@

We now turn to an illustration of our theory with the analysis of an empirical
dataset of host–parasite networks sampled throughout the south–north
environmental gradient in continental Europe \citep{Kopelke2017}. Our
objective here is to illustrate potential applications of the approach
outlined above, rather than a specific attempt at describing the biogeography
of this particular community. The focal system consists of local food webs of
willows (genus \textit{Salix}), their galling insects, and the natural enemies
(parasitoids and inquilines) of these gallers. We ask:
i) how much does network structure vary across the gradient, and ii) what is
the primary driver of network turnover across the gradient?

@@

Communities of willows, gallers, and parasitoids are species-rich and widely
distributed, with pronounced variation in community composition across space.
The genus \textit{Salix} includes over 400 species, most of which are shrubs
or small trees \citep{Argus1997}, and is common in moist habitats across the
Northern Hemisphere \citep{Skvortsov1999}. Willows support a highly diverse
community of herbivorous insects, with one of the main herbivore groups being
gall- inducing sawflies (Hymenoptera: Tenthredinidae: Nematinae: Euurina
\citep{Kopelke1999}). Gall formation is induced by sawfly females during
oviposition, and includes marked manipulation of host-plant chemistry by the
galler \citep{Nyman2000}. The enemy community of the gallers includes nearly
100 species belonging to 17 insect families of four orders
\citep{Kopelke2003}. These encompass two main types: inquiline larvae
(Coleoptera, Lepidoptera, Diptera, and Hymenoptera) feed primarily on gall
tissue, but typically kill the galler larva in the process, while parasitoid
larvae (representing many families in Hymenoptera) kill the galler larvae by
direct feeding \citep{Kopelke2003}.

@@

The current study represents the first analysis of the full data set
from a spatial perspective. Full details about the data collection and species
identification are provided in \citep{Kopelke2017}. Annual mean temperature
and precipitation were obtained from WorldClim using the R package dismo
\citep{Hijmans2015} and GPS coordinates of the sampling locations. While other
covariates could have also been considered to represent the high
dimensionality of the niceh, these two variables are likely representative of
the most important axes of the European climate, and are also more easily
interpretable than reduced variables obtained, for example, by principal
component analysis.

@@

Once we had selected the best model based on AIC (Model 3, Table 2), we used
it to reconstruct the expected species richness, along with the most likely
network for each location. Using this approach, we mapped the expected
distribution of network properties across Europe (Fig. 6). For simplicity, we
chose to consider connectance as our descriptor of network configuration, as
this metric can be easily computed from probabilistic networks
\citep{Poisot2015c} and is also a good proxy for many other network properties
\citep{Poisot2014}. Overall, we found a peak in \textit{Salix}, gallers and
parasitoid diversity in Northern Europe. The expected number of interactions
roughly followed the distribution of species richness, but accumulated at a
rate different from species numbers. Connectance likewise peaked in Northern
Europe (Fig. 6).

>>>>

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{color,lineno,setspace,multirow}
\usepackage{graphicx}
\usepackage[top=2.4cm,left=2.4cm,top=2.4cm,bottom=2.4cm,includefoot]{geometry}
\usepackage{natbib}
\usepackage{caption}
\usepackage{pdflscape}
\usepackage{hyperref}

@@

Biogeography has traditionally focused on the spatial distribution and
abundance of species. Both are driven by the way species interact with one
another, but also by the way these interactions vary across time and space.
Here, we call for an integrated approach, adopting the view that community
structure is best represented as a network of ecological interactions, and
show how it translates to biogeography questions. We propose that the
ecological niche should encompass the effect of the environment
on species distribution (the Grinnellian dimension of the niche) and on the
ecological interactions among them (the Eltonian dimension). Starting from
this concept, we develop a quantitative theory to explain turnover of
interactions in space and time -- \emph{i.e.} a novel approach to interaction
distribution modeling. We apply this framework to host–parasite interactions
across Europe and find that two aspects of the environment (temperature and
precipitation) exert a strong imprint on species co-occurrence, but not on
species interactions. Even where species co-occur, interaction proves to be
stochastic rather than deterministic, adding to variation in realized network
structure. We also find that a large majority of host-parasite pairs are never
found together, thus precluding any inferences regarding their probability to
interact. This first attempt to explain variation of network structure at
large spatial scales opens new perspectives at the interface of species
distribution modeling and community ecology.

@@

Community ecology is \textit{the study of the interactions that determine the
distribution and abundance of organisms} \citep{Krebs2001}. Despite a general
consensus on this definition \citep{Scheiner2007a}, research on variation in
community structure (beta-diversity) has mostly focused on the spatial and
temporal turnover of species composition \citep{Anderson2011}. Such research
usually neglects variation in the way species interact with each other,
despite accumulating empirical evidence that is a major source of
diversity \citep{Poisot2015a}. Given this omission, it is perhaps not
surprising that biogeographers are still struggling to establish whether
interactions actually impact the distribution of species at large spatial
scales \citep{Kissling2012}. An interaction is conceived as the direct effect
of the action of one species on the demography on another species; whether it
scales up and impact the (co-)distribution of species remains matter of debate
at the moment \citep{Wisz2012, GonzalezSalazar2013, Cazelles2016b,
Harris2016, Godsoe2017}. Treating interactions as fixed events nonetheless
neglects a large part of the complexity of empirical communities, and will
most likely deliver biased metrics \citep{Poisot2015c}. Recent attempts
at accounting for interactions in species distribution models
\citep{Pollock2014, Pelissier2013, Ovaskainen2017} have brought some
methodological advances, but are not sufficient for two reasons. First, these
techniques are still based on a `species-based' approach to communities, where
interactions are merely treated as fixed covariates affecting distribution.
Second, they failed to provide a conceptual step forward, both in their
treatment of interactions and in the quality of the predictions they make.

Network approaches offer a convenient representation of communities because
they simultaneously account for species composition and their interactions.
Species are represented as nodes, so that networks already encompass all the
information used by current approaches of species distribution modeling; in
addition, interactions are represented by links, so that networks provide
additional information on community structure. To date, studies of network
diversity have mostly been concerned with the distribution of interactions
within locations, and less so with variation among locations \citep{Dunne2006,
Bascompte2007, Ings2009, Kefi2012}. There is, however, ample evidence that
interaction networks vary in space and time \citep{Laliberte2010, Poisot2012,
Schleuning2012, Albouy2014, Poisot2016, Trojelsgaard2015}, even though there
is no common framework with which to generalize these results. Metacommunity
theory provides explanations for variation in the distribution of the nodes
\citep{Gravel2011c, Pillai2011,Cazelles2015}, but there are no such explanation
to the variation of node and link occurrences. Consequently, we need theory to
formalize these observations, as it is the only way towards fulfilling the
goal of community ecology: providing cogent predictions about, and
understanding of, the structure of ecological communities.

Given the historically different approaches to modelling the distributions of
species vs. interactions, there is a need to bring the two together. Here, we
offer an integrated approach to do so, adopting the view that community
structure is best represented as a network of ecological interactions. Based
on this idea, we propose a description of the ecological niche that
integrates the effect of the environment on species distribution and on the
ecological interactions among them. Building on this concept, we develop a
quantitative theory to explain turnover of interactions in space and time. We
first present the concept and then formalize it mathematically, using a
probabilistic model to represent the sampling of the regional pool of
interactions. At the level of species pairs, the statistical approach could be
conceived as an interaction distribution model. At the community level, the
approach provides a likelihood-based method to compare different hypotheses of
network turnover. As an illustrative example, we apply this novel framework to
a large data set on host–parasite interactions across Europe and find that two
aspects of the environment (temperature and precipitation) exert a strong
imprint on species co-occurrence, but not on species interactions. The network
structure changes systematically across the latitudinal gradient, with a peak
of connectance at intermediate latitudes.

@@

The problem of community assembly is often formulated as \textit{how are
species sampled from a regional pool to constitute a local community
\citep{Gotzenberger2012}?} This question could be rewritten to address the
problem of network assembly, as \textit{how do samples from a regional pool of
interactions constitute a local interaction network?} An illustration of this
problem for a food web is provided in Fig. 1. The regional pool of
interactions, the \emph{metaweb}, represents potential interactions among all
species that could be found in a given area. In this particular case, there
are 275 nodes, and 1173 links among the plants (52 nodes), herbivores (96
nodes), and parasitoids (127 nodes) from Northern Europe. An instance of a
local community is also illustrated, with 45 nodes and 93 interactions. Only
55.0\% of all potential interactions (plant-herbivore or herbivore parasitoid
combinations) are realized in this local network, revealing the stochastic
nature of ecological interactions. Our objective here is to provide theory to
explain the sampling of the regional pool of interactions, along with a
quantitative method to predict it. The problem could be formalized
sequentially by understanding first why only a fraction of the species co-occur locally and second why these species do or do not interact.

There are multiple causes of spatial turnover of species co-occurrence. The
first and most-studied driver is the effect of variation in the abiotic
environment on species performance. Combined with specific responses in
demography, it generates variation among sites by selecting the locally
fittest species \citep{Leibold2004a}. Stochasticity plays an additional role,
either because colonization and extinction events \citep{Hanski1999} are
inherently unpredictable or because strong non-linear feedbacks in community
dynamics generate alternative transients and equilibria \citep{Chase2007,
Vellend2014}. Interaction themselves may impact co-distribution, as
hypothesized long ago by \citet{Diamond1975}. Analyses of community
turnover are usually performed with data represented in a table with rows
corresponding to sites (or measurements) and columns to species. Metrics of
beta diversity quantify the variance of this community data
\citep{Legendre2005}. Traditional approaches rely on measures of dissimilarity
among communities, such as the Jaccard or Bray–Curtis indices. More recent
approaches decompose total variation of the community data into species and
site contributions to beta diversity \citep{Legendre2013}, and further
partition it into dissimilarity due to changes in species richness and
dissimilarity due to actual species turnover \citep{Baselga2010}. Even
though all of these methods compare whole lists of species among sites or
measurements, they remain fundamentally "species-based", since they report
variation within columns. None of them explicitly considers variation of
associations (i.e., of pairs or higher-order motifs – \citealt{Stouffer2007}).
The only exceptions are the Joint Species Distribution Models
\citep{Warton2015, Ovaskainen2017}, which further account for the covariance
among species after representing their response to the environment.

We are now getting a better understanding of interaction turnover. As
mentioned above, in the network approach to community structure, species and
interactions are represented by nodes and links, respectively. Associations
can also be represented by matrices in which entries represent the occurrence
or intensity of interactions among species (rows and columns). Network
complexity is then computed as the number of interactions (in the case of
binary networks) or interaction diversity (in the case of quantitative
networks, \citealt{Bersier2002}). Variability in community structure
consequently arises from the turnover of species composition, along with
turnover of interactions among pairs of species. The occurrence and intensity
of interactions could vary because of the environment, species abundance, and
higher-order ecological interactions \citep{Poisot2015a}. Variation in community
composition can be independent of variation of ecological
interactions, suggesting that species and interaction distribution may well
respond to different drivers \citep{Poisot2012}.

The "niche" is by far the dominant concept invoked to explain species
distributions and community assembly, from the local to the global scale.
Following \citet{Hutchinson1957}, the niche is viewed as the set of
environmental conditions allowing a population to establish and persist (see
also \citealt{Holt2009a}). In other words, the niche is the location in that
multidimensional space allowing a species to have a positive growth rate
when rare \citep{Godsoe2017}.  Community turnover arises as a result of
successive replacement of species along an environmental gradient, in
agreement with the Gleasonian view of communities \citep{Gleason1926}. The
concept is straightforward to put into practice with species distribution
models, as it maps naturally on available distributional and environmental
data. Consequently, a vast array of statistical tools have been developed to
implement it (e.g. BIOMOD \citealt{Thuiller2003}, MaxEnt
\citealt{Phillips2006}). It is however much harder to account for ecological
interactions within this approach \citep{Peterson2011}. As such, these
interactions are often viewed as externalities constraining or expanding the
range of environmental conditions required for a species to maintain a viable
population \citep{Pulliam2000, Soberon2007}.

@@

Despite several attempts to update the concept of the ecological niche,
ecologists have not moved far beyond the "n-dimensional hypervolume" defined
by \citet{Hutchinson1957}. Despite its intuitive interpretation and easy
translation into species distribution models \citep{Boulangeat2012,
Blonder2014}, the concept has been frequently criticized \citep{Hardin1960,
Peters1991, Silvertown2004}, and several attempts have been made to expand and
improve it \citep{Pulliam2000, Chase2003, Soberon2007, Holt2009a,
McInerny2012b}.

@@

These perspectives are rather orthogonal to each other, and this has resulted
in considerable confusion in the literature \citep{McInerny2012a}.
\citealt{Chase2003} attempted to reconcile with the following definition:
\emph{"[The niche is] the joint description of the environmental conditions that
allow a species to satisfy its minimum requirements so that the birth rate of
a local population is equal to or greater than its death rate along with the
set of per capita effects of that species on these environmental conditions"}.
Their representation merges zero-net-growth isoclines delimiting the
Grinnellian niche ("when does the population persist?") with impact vectors
delimiting the Eltonian niche ("what is the per-capita impact?"). While this
representation has been very influential in local-scale community ecology (the
resource-ratio theory of coexistence, \citealt{Tilman1982}), it remains
impractical at larger spatial scales because of the difficulties in measuring
it. The absence of any mathematical representation of the niche that can be
easily fit to ecological data may explain why biogeographers are still
struggling to develop species distribution models that also consider
ecological interactions. Thus, a more integrative description of the niche
will be key to understand spatial and temporal turnover in community
structure.

We propose to integrate the two perspectives of the niche using a visual
representation of both components (Fig. 2). The underlying rationale is that,
in addition to the environmental constraints on demographic performance (Fig. 2,
top panel), any organism requires resources to meet its metabolic demands and
to sustain reproduction (Fig. 2, nodes in network of bottom panel). Abiotic
environmental axes are any non-consumable factors affecting the demographic
performance of an organism. Alternatively, the resource axes are traits of the
resources that allow interactions with the consumers. By definition of what an
interaction is, these axes also influence the growth rate. The niche can
therefore be viewed as the set of abiotic environmental conditions (the
Grinnellian component) along with the set of traits (the Eltonian component)
that allow a population to establish and to grow at a location. This visual
representation make operational the theoretical interpretation of the niche
and species ranges by \citet{Godsoe2017}. Accordingly, each
species can be characterized by an optimal position along both the
environmental (x-axis) and the trait (y-axis) plane. The integrated niche is
then the hypervolume where interactions can occur and where a population has a
positive growth rate.

@@

The first term on the right-hand side of the equation is the probability
of observing the two species co-occurring at location $y$. It corresponds
to the Grinnellian dimension of the niche. The second term represents the
probability that an interaction occurs between species $i$ and $j$, given that
they are co-occurring. This predicate can be refined using information on
trait distribution and trait matching rules \citep{Bartomeus2016}.
Above, we referred to this entity as the "metaweb" and it corresponds to
the Eltonian dimension of the niche. Below, we will see how this formalism
can be directly fit to empirical data. But before turning to an application,
we will discuss the interpretation of different variants of these two terms.

@@

There are several variants to the co-occurrence probability, representing
different hypotheses concerning spatial variation in network structure (see
the explicit formulations in Table 1). The simplest model relates the
probability of co-occurrence directly to the environment,
$P(X_{iy},X_{jy}|E_y)$. In this situation, there are no underlying assumptions
about the ecological processes responsible for co-occurrence. Spatial associations between species could arise
because interactions constrain distribution, where in such case the co-occurrence would be conditional on $L$, or, alternatively, because of
environmental requirements shared between $i$ and $j$ \citep{Pollock2014,
Cazelles2016}. In the former case, species are not independent of each other
and the conditional occurrence must be accounted for explicitly,
$P(X_{iy},X_{jy} |E_y)=P(X_{iy}|E_y,X_{jy})P(X_{jy}|E_y)$. In the latter case,
species are independent, and only the marginal occurrence must be accounted
for, $P( X_{ijy}|E_y)=P(X_{iy} |E_y)P(X_{jy} |E_y)$.

The co-occurrence probability itself could depend on ecological interactions. 
This should be viewed as the realized component of the niche (i.e. the
distribution when accounting for species interactions). Direct pairwise
interactions such as competition, facilitation, and predation have long been
studied for their impact on co-distribution (e.g. \citealt{Diamond1975,
Connor1979, Gotelli2000}). Second- and higher-order interactions (e.g. trophic
cascades) could also affect co-occurrence \citep{Harris2016,
Staniczenko2017}. Co-occurrence of multiple species embedded in ecological
networks is a topic of its own, however, and is influenced by both network
topology and species richness \citep{Cazelles2016}. Not only direct
interactions influence co-occurrence, but indirect interactions do as well
(e.g. plant species sharing an herbivore, or herbivores sharing parasitoids,
could repel each other in space \citep{Holt1993}). The impact of direct
interactions and first-order indirect interactions on co-occurrence tends to
vanish with increasing species richness in the community \citep{Cazelles2016}.
Further, co-occurrence is also influenced by the covariance of interacting
species to an environmental gradient \citep{Cazelles2015}.

@@

Second, ecological interactions could also vary with the environment, so that
$P(L_{ijy}|E_y)$. Although it is rare to see a conditional representation of
pairwise ecological interactions, experimental studies have frequently
revealed interactions to be sensitive to the environment. For instance,
\citet{Mckinnon2010} showed that predation risks of shorebirds vary at the
continental scale, decreasing from the south to the north. It is also common
to see increasing top-down control with temperature (e.g. \citealt{Shurin2012,
Gray2016}). Effects of the environment on interactions \citep{Gibert2014} also
propagate up the community and influence network structure
\citep{Tylianakis2007, Woodward2010, Petchey2010a}.

@@

We now turn to an illustration of our theory with the analysis of an empirical
dataset of host–parasite networks sampled throughout the south–north
environmental gradient in continental Europe \citep{Kopelke2017}. Our
objective here is to illustrate potential applications of the approach
outlined above, rather than to specifically describe the biogeography
of this particular community. The focal system consists of local food webs of
willows (genus \textit{Salix}), their galling insects, and the natural enemies
(parasitoids and inquilines) of gallers. We ask:
i) how much does network structure vary across the gradient, and ii) what is
the primary driver of network turnover across the gradient?

@@

Communities of willows, gallers, and parasitoids are species-rich and widely
distributed, with pronounced variation in community composition across space.
The genus \textit{Salix} includes over 400 species, most of which are shrubs
or small trees \citep{Argus1997}, and is common in moist habitats across the
Northern Hemisphere \citep{Skvortsov1999}. Willows support a highly diverse
community of herbivorous insects, with one of the main herbivore groups being
gall-inducing sawflies (Hymenoptera: Tenthredinidae: Nematinae: Euurina
\citep{Kopelke1999}. Gall formation is induced by sawfly females during
oviposition, and includes marked manipulation of host-plant chemistry by the
galler \citep{Nyman2000}. The enemy community of the gallers includes nearly
100 species belonging to 17 insect families of four orders
\citep{Kopelke2003}. These encompass two main types: inquiline larvae
(Coleoptera, Lepidoptera, Diptera, and Hymenoptera) feed primarily on gall
tissue, but typically kill the galler larva in the process, while parasitoid
larvae (representing many families in Hymenoptera) kill the galler larvae by
direct feeding \citep{Kopelke2003}.

@@

The current study represents the first analysis of the full data set
from a spatial perspective. Full details about data collection and species
identification are provided in \citep{Kopelke2017}. Annual mean temperature
and precipitation were obtained from WorldClim using the R package dismo
\citep{Hijmans2015} and GPS coordinates of the sampling locations. While other
covariates could have also been considered to represent the high
dimensionality of the niche, these two variables are likely representative of
the most important axes of European climate, and are also more easily
interpretable than reduced variables obtained, for example, by principal
component analysis.

@@

Once we had selected the best model based on AIC (Model 3, Table 2), we used
it to reconstruct the expected species richness, along with the most likely
network for each location. Using this approach, we mapped the expected
distribution of network properties across Europe (Fig. 5). For simplicity, we
chose to consider connectance as our descriptor of network configuration, as
this metric can be easily computed from probabilistic networks
\citep{Poisot2015c} and is also a good proxy for many other network properties
\citep{Poisot2014}. Overall, we found a peak in \textit{Salix}, gallers and
parasitoid diversity in Northern Europe. The expected number of interactions
roughly followed the distribution of species richness, but accumulated at a
rate different from species numbers. Connectance likewise peaked in Northern
Europe (Fig. 5).
